\ttlfnt{Comparing the performance of websites and their content distribution networks}

### 2016-08-28 Writeup/paper.tex
Minor improvement to sentence
Add conclusions to abstarct

\begin{abstract}
Modern internet infrastructure consists of deep hierarchies of caches and Content Delivery Networks in order to serve the ever-increasing demand for high-bandwidth multimedia content. In this report we present a tool for measuring the impact of Content Delivery Networks on the performance of streaming video and audio content over the internet. We analyse the performance impact of these networks from the point of view both of the home user and large-scale institutions.
\end{abstract}

@@

We tested from a number of ISPs on a home network as well as an institutional network. Our results gained insights on the caching behaviour of YouTube with respect to videos with very few views. We found that the majority of unpopular videos are not cached within South Africa. The video has to be obtained from a Google cache in Europe. We found that after viewing the unpopular video it would be cached on both on the ISP's server and Google's South African cache. Subsequent views from the same ISP would come from the ISP cache and views from another ISP would come from Google's South African cache instead of from Europe.

>>>>

\begin{abstract}
Modern internet infrastructure consists of deep hierarchies of caches and Content Delivery Networks in order to serve the ever-increasing demand for high-bandwidth multimedia content. In this report we present a tool for measuring the impact of Content Delivery Networks on the performance of streaming video and audio content over the internet. We analyse the performance impact of these networks from the point of view both of the home user and large-scale institutions. We find that the majority of unpopular videos are not cached within South Africa. The video has to be obtained from a Google cache in Europe. We find that after viewing the unpopular video it is cached on both on the ISP's server and Google's South African cache. Subsequent views from the same ISP come from the ISP cache and views from another ISP come from Google's South African cache instead of from Europe. On the institutional network we find that even though, on the second execution, an unpopular YouTube video is obtained from the institution's cache, the throughput is always slower than the third execution.
\end{abstract}

@@

We executed our tool on various multimedia services using a number of ISPs on a home network as well as an institutional network. Our results gained insights on the caching behaviour of YouTube with respect to videos with very few views. We found that the majority of unpopular videos are not cached within South Africa. The video has to be obtained from a Google cache in Europe. We found that after viewing the unpopular video it would be cached on both on the ISP's server and Google's South African cache. Subsequent views from the same ISP would come from the ISP cache and views from another ISP would come from Google's South African cache instead of from Europe.
